# Google Deepmind Internships {#deepmind}

(ref:yourfutureblurb)

## Deepmind Internships in Manchester {#deepmanchester}

Looking for a summer internship in AI? The Centre for AI Fundamentals [www.ai-fun.manchester.ac.uk](https://www.ai-fun.manchester.ac.uk/) is now accepting applications from undergraduates or recent graduates who have the potential to become the future of research in Artificial Intelligence and Machine Learning. The closing date for these is **Friday 21st March**.

```{r, eval=knitr::is_html_output(excludes = "epub"), results='asis', echo=FALSE}
cat('<iframe src="https://www.linkedin.com/posts/duncanhull_raeng-google-deepmind-internships-ellis-activity-7300915014704467969-73B3" height="1116" width="504" frameborder="0" allowfullscreen="" title="Embedded post"></iframe>')
```

## Deepmind Internships across the UK {#deepuk}

The internships are part of wider UK scheme, closing dates vary with institutions, see below.

```{r, eval=knitr::is_html_output(excludes = "epub"), results='asis', echo=FALSE}
cat('<iframe src="https://www.linkedin.com/posts/duncanhull_google-deepmind-research-ready-activity-7301226312621314048-z04n" height="1116" width="504" frameborder="0" allowfullscreen="" title="Embedded post"></iframe>')
```
